Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-09 cmsb22.tex
Add two missing results

\end{document}

>>>>

\section{Selected models}

\begin{table}[!htb]
  \caption{Timing comparisons between the proposed method and PyBoolNet on selected models from the literature.
    Columns "\(n\)", "\(e\)", and "\(s\)" denote the numbers of nodes, interactions, and source nodes of each model, respectively. Column "\(|M|\)" denotes the number of minimal trap spaces and for each method is given the computation time in seconds.
    "DNF" means that the method did not finish the computation (with a maximum of 1000 trap spaces) within the timeout of 2 minutes. Number in bold indicate a ratio greater than three.}
  \centering
  \label{tab:selected_redone}
  \begin{tabular}{lrrrrrr}
    \toprule
    model & $n$ & $e$ & $s$ & $|M|$ & PyBoolNet (s) & Trappist (s) \\ \midrule
    CASCADE3 & 183 &&& 1 & 118.54 & 1.03\\
    KYNURENINE-PATHWAY & 150 &&& 1 & 102.45 & 1.09\\
    SN5 & 2746 &&& ??? & DNF & DNF\\
    ERBB-RECEPTOR-SIGNALING & 247 &&& 1000+ & DNF & 3.56\\
    Executable\_file\_for\_cholocystokinin\_model & 404 &&& 1000+ & 1.46 & 1.79\\
    korkut\_2015a & 99 &&& 1000+ & DNF & 0.56\\
    SIGNALING-PATHWAY-FOR-BUTANOL-PRODUCTION & 66 &&& 1 & 0.24 & 0.16\\
    Corral\_ThIL17diff\_15jan2021 & 92 &&& 1000+ & DNF & 0.32\\
    HIV-1 & 138 &&& 6 & DNF & 0.33\\
    Executable\_file\_for\_CaSQ\_derived\_mast\_cell\_activation\_model & 80 &&& 1000+ & 0.89 & 0.17\\
    Colitis\_associated\_colon\_cancer & 70 &&& 5 & 0.22 & 0.07\\
    INTERFERON-1 & 121 &&& 2 & 13.21 & 0.12\\
    TLGLSurvival & 61 &&& 3 & 0.73 & 0.16\\
    cho\_2016\_all\_pos & 200 &&& 1000+ & DNF & 0.64\\
    turei\_2016 & 4691 &&& ??? & DNF & DNF\\
    Human\_network & 1953 &&& 1000+ & DNF & 42.58\\
    Executable\_file\_for\_CaSQ\_derived\_MAPK\_model & 182 &&& 1000+ & DNF & 0.32\\
    TCR-TLR5-SIGNALING-2018 & 130 &&& 48 & 1.52 & 0.17\\
    Hernandez\_TcellCheckPoints\_13april2020 & 218 &&& 1000+ & 53.51 & 0.55\\
    IMMUNE-SYSTEM & 164 &&& 1000+ & DNF & 0.92\\
    HMOX1-PATHWAY & 145 &&& 8 & 3.72 & 0.11\\
    Signaling\_in\_Macrophage\_Activation & 321 &&& 1 & 13.25 & 0.31\\
    FIBROBLASTS & 139 &&& 1000+ & DNF & 0.61\\
    S1\_Table & 1659 &&& 1000+ & DNF & 58.98\\
    Regan2020\_Adhesion\_CIP\_Migration\_CellCycle\_Apoptosis & 121 &&& 78 & 53.30 & 0.53\\
    SIGNALING-IN-PROSTATE-CANCER & 133 &&& 1000+ & DNF & 0.46\\
    InflammatoryBowelDisease & 47 &&& 1 & DNF & 33.02\\
    Influenza\_A\_Virus\_Replication\_Cycle & 131 &&& 17 & 51.17 & 0.13\\
    IL\_6\_Signalling & 86 &&& 1 & 0.49 & 0.07\\
    VIRUS-REPLICATION-CYCLE & 154 &&& 2 & DNF & 0.19\\
    Executable\_file\_for\_Alzheimer\_model & 1169 &&& 1000+ & DNF & 1.53\\
    ER-STRESS & 182 &&& 32 & 31.99 & 0.21\\
    RA\_apoptosis\_executable\_module & 180 &&& 1000+ & DNF & 0.23\\
    \bottomrule
  \end{tabular}
\end{table}

\sylvain{Some models seem to have a different number of trap spaces here than in the other table (like RA apoptosis), for others quite large time differences (ERBB, inflammatory bowel)\dots}
\end{document}
